Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-13 paper/main.tex
revise annotation related tables

\item confound regressors von modeling hoch zu eventes

\item revise captions of Table 1 + 3

@@

\todo[inline]{SE: focus on the events that are relevant to the analysis to
reduce complexity and explain these better; COH: revised but maybe still not
``optimal''}

@@

\paragraph{AV confounds}

% visual confounds -> cf. table

% audio-track confounds
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.

\todo[inline]{SE: Continuous bins lasting 40ms?}

@@

    \caption{Overview of events to build the 14 regressors for the analysis of
        the audio-visual (AV) stimulus.

@@

        For description of the two event categories of the audio-description's
        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
        negative control see Table
\ref{tab:ao-events}.}

@@

se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII

@@

fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Lastly, some noun categories that were semantically similar and offered only a
small amount of counts were pooled resulting in 11 final event categories (see
Table \ref{tab:ao-events}). These event categories were then used to model
hemodynamic responses.

\paragraph{AD confounds}

% audio confounds -> cf. AV & table

% final reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the descriptive nouns spoken by
        the audio-description's narrator. Some of these initial 18 noun
        categories were pooled resulting in 11 event categories that served as
        a basis to build the regressors of the GLM
        (cf. Table \ref{tab:ao-events}).
        Examples are given in English.
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe
\tabularnewline
face & face or parts of it & face, ear, nose, mouth
\tabularnewline
female & female person & nurse, mother, woman
\tabularnewline
females & female persons & women
\tabularnewline
fname & female name & Jenny
\tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet
\tabularnewline
male & male person & man, father, soldier
\tabularnewline
males & male persons & boys, opponents
\tabularnewline
mname & male name & Bubba, Kennedy
\tabularnewline
object & countable entity with firm boundaries & telephone, car
\tabularnewline
objects & countable entities & wheels, plants
\tabularnewline
persons & concrete persons of unknown sex & hippies, patients
\tabularnewline
setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    \caption{Overview of events to build the 18 regressors for the
        analysis of the audio-only (AD) stimulus. Some of the annotation's
        original categories (female, females, fname; male, males, mname; face,
        head; object, objects; see Table\ref{tab:descr-nouns-rules}) were pooled
        into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
        \texttt{fahead}; \texttt{object}).  \texttt{fg\_ad\_lrdiff} (left-right
        volume difference) and \texttt{fg\_ad\_rms} (root mean square volume)
        represent one event for every movie frame (\unit[40]{ms}). For a
        description of the five control conditions for movie cuts see Table
        \ref{tab:av-events}.}

@@

vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII &
\aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII &
\aoVsenewVIII
vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
vlo\_ch & control for movie cut &
\aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV
& \aoVlochVI & \aoVlochVII
vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII

@@

vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 &
\aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII

@@

fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll &

@@

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events [lenght = 20 ms?].\todo[actually, that might not be
true}

>>>>

\item revise captions of Table 1 + 3; regressors that are based on the other
    stimulus for control purposes are now dropped from the table; but mention in
        Statistical Analysis / Statistical Model)

@@

@@

@@

    \caption{Overview of annotations and event counts in the whole audio-visual
    movie and individual stimulus segments.

@@

    % For description of the two event categories of the audio-description's
    % narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
    % negative control see Table \ref{tab:ao-events}.
    }

@@

% se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
% \tabularnewline
% se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
% \tabularnewline

@@

fg\_av\_ger\_rms & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a
small amount of counts were pooled resulting in 11 final event categories (see
Table \ref{tab:ao-events}). These event categories were then used to model
hemodynamic responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the descriptive nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as a basis to build the regressors of the
        GLM
        (cf. Table \ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe
\tabularnewline
face & face or parts of it & face, ear, nose, mouth
\tabularnewline
female & female person & nurse, mother, woman
\tabularnewline
females & female persons & women
\tabularnewline
fname & female name & Jenny
\tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet
\tabularnewline
male & male person & man, father, soldier
\tabularnewline
males & male persons & boys, opponents
\tabularnewline
mname & male name & Bubba, Kennedy
\tabularnewline
object & countable entity with firm boundaries & telephone, car
\tabularnewline
objects & countable entities & wheels, plants
\tabularnewline
persons & concrete persons of unknown sex & hippies, patients
\tabularnewline
setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    \caption{Overview of annotations and event counts in the whole
    audio-description and individual stimulus segments.
    Some of the annotation's original categories (female, females, fname; male,
    males, mname; face, head; object, objects;
    see Table\ref{tab:descr-nouns-rules}) were pooled
    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead};
    \texttt{object}), \texttt{fg\_ad\_lrdiff} (left-right volume difference)
    and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for
    every movie frame (\unit[40]{ms}).
    % For a description of the five control conditions for movie cuts see
    % Table \ref{tab:av-events}.
    }

@@

%vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
%\tabularnewline
%vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
%\tabularnewline
%vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
%\tabularnewline
%vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
%\tabularnewline

@@

%vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
% \tabularnewline

@@

fg\_ad\_rms & root mean square volume & \aoFgadrmsAll &

@@

\paragraph{Confounds for both}

\todo[inline]{Die Events für die low-level confounds habe erstmal hier
beschrieben; btw: Das Verschieben des Sounds in den Segmenten spiegelt sich
wahrscheinlich auch in den unterschiedlichen Counts der Events je Segment wider
(AV Bild vs AV Sound vs AO Sound)}

% intro
Lastly, we algorithmically annotated the temporal
structure of low-level perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual differene of consecutive frames.
% auditory shit
Finally, we computed the left-right difference in volume and root mean
square energy averaged across the length of every movie frame (\unit[40]{ms}) of
both audio-tracks.

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events [lenght = 20 ms?].\todo{actually, that might not be
true}
